Predicting The Success of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics Using Mean and Standard Deviation Derived Parameters

### 2024-01-10 manuscript/submission.tex
revising the appendix to only include essential content on the mens component

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{MaleAthleteApparatus.pdf}
  \caption{Top 10 Male Candidates for the Olympic Floor Exercise, Pommel Horse, Still Rings, Vault, Parallel Bars, 
  and High Bar Apparatus}
  \label{fig:FA}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.7]{MaleMultipleAllAround.pdf}
  \caption{The best candidates for the male individual all-around and team all around medals}
  \label{fig:FAA}
\end{figure}

@@

When determining the most ideal American male candidates, 
I did inspect the data of non United States gymnasts in order to determine which medals the United States 
male team has the greatest chance of earning.

Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 
Figure~\ref{fig:IAAM} I determined that Juda and Malone are the best male Individual all-around candidates. From 
Figure~\ref{fig:MAA3} I determined that Juda, Malone, and Young are the best male team all-around finalists 
candidates. Additionally, from Figure~\ref{fig:MAA4} I determined that Moldauer is the best candidate to also compete 
with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the ``best'' fifth Olympic 
teammate is challenging as there are several apparatuses where our ``best'' competitor is not among the four 
previously selected teammates. However, through examining the the mean score for every male gymnast on every apparatus 
we can see that many of our ``best'' candidates are still ranked very poorly globally, and therefore would not have a 
strong liklihood of medalling at the olympics. Among all of the male USA athletes that are not yet selected, the only 
athlete that has a relatively decent chance of medaling is Hale, who ranks 6th globally for the Vault apparatus.

Ultimately, in order to maximize the the number of medals the Unites States male team wins, I would comprise the 
team of the athletes Juda, Malone, Young, Moldauer, and Hale.

Based on the plot of the top ten male athletes on the floor exercise apparatus I selected the parameter of 
the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' male athletes on floor exercise are Juda, Mccool, Young, Moldauer, 
and Hong.

Based on the plot of the top ten male athletes on the vault apparatus I selected the parameter of 
the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' male athletes on vault are Hale, Young, Malone, Briones, and 
Juda.

Based on the plot of the top ten male athletes on the still rings apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' male athletes on still rings are Whittenburg, Briones, Diab, 
Hong, and Loos.

Based on the plot of the top ten male athletes on the pommel horse apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' male athletes on pommel horse are Nedoroscik, Young, Malone, 
Dang, and Bock.

Based on the plot of the top ten male athletes on the parallel bars apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' male athletes on parallel bars are Hong, Chou, Walker, Malone, 
and Phillips.

Based on the plot of the top ten male athletes on the high bar apparatus I selected the parameter of 
half of the score standard deviation subtracted from the mean score in order to identify the best suited five 
athletes. Based on the parameter, the five ``best'' male athletes on high bar are Malone, Juda, Briones, Bold, and 
Nguyen.

Ultimately, the list of athletes that ranked among the top five United States male athletes 19 distinct 
names. However, nine of these athletes have not competed on all six apparatuses, so they will not be considered 
with the other ten athletes for individual or team all-around. Thus, the list of selected athletes that 
are involved in future computations includes Juda, Young, Moldauer, Hong, Hale, Malone, Whittenburg, Loos, 
Bock, and Walker.

>>>>

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{MaleAthleteApparatus.pdf}
  \caption{Top 10 Male Candidates for the Olympic Floor Exercise, Pommel Horse, Still Rings, Vault, Parallel Bars, 
  and High Bar Apparatus}
  \label{fig:MA}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.7]{MaleMultipleAllAround.pdf}
  \caption{The best candidates for the male individual all-around and team all around medals}
  \label{fig:MAA}
\end{figure}

@@

Similar to the female model, I used the same method to determine the ``best'' male all-around candidates as I did for females. From 
Figure~\ref{fig:MAA} I determined that Juda and Malone are the best male Individual all-around candidates, 
Juda, Malone, and Young are the best male team all-around finalists, and Moldauer is the best candidate to also compete 
with Juda, Malone, and Young in the all-around qualifying round. Comparatively, determining the ``best'' fifth Olympic 
teammate is challenging as there are several apparatuses where our ``best'' competitor is not among the four 
previously selected teammates. However, through examining the the mean score for every male gymnast on every apparatus 
we can see that many of our ``best'' candidates are still ranked very poorly globally, and therefore would not have a 
strong liklihood of medalling at the Olympics. Among all of the male USA athletes that are not yet selected, the only 
athlete that has a relatively decent chance of medaling is Hale, who ranks 6th globally for the Vault apparatus.

Ultimately, in order to maximize the the number of medals the Unites States male team wins, the team should be comprised  
of the athletes Juda, Malone, Young, Moldauer, and Hale.
